{\Huge Supersymmetry} \\ \vspace{5mm} Lecture notes for FYS5190/FYS9190 Supersymmetry

### 2025-10-08 superspace.tex
Fixes for lecture 15

To understand what all of this means we start from the same perspective as for the four-vectors in the previous section, and begin by writing a general element of SP, $g\in SP$, using the exponential map defined in Section \ref{sec:lie_algebras}:
\[g = \exp\left(ix^\mu P_\mu + i\theta^{A} Q_A + i\bar{\theta}_{\dot{A}}\bar{Q}^{\dot{A}} + \frac{i}{2}\omega_{\rho\nu}M^{\rho\nu}\right),\]
where $x^\mu$, $\theta^{A}$, $\bar{\theta}_{\dot{A}}$ and $\omega_{\rho\nu}$ constitute the parametrisation of the group, and $P_\mu$, $Q_A$, $\bar Q^{\dot{A}}$ and $M_{\rho\nu}$ are the generators. Following the same argument as above we can now parametrise the coset space $SP/L$ simply by setting $\omega_{\mu\nu} = 0$.\footnote{$SP/L$ is again {\it not} a coset group, because $L$ is not a normal subgroup of $SP$, but it still forms a vector space (the coset space) which we call superspace.} The remaining parameters of $SP/L$ are then the coordinates that span superspace.

@@

We now want to find the effect of supersymmetry transformations (transformations by the super-Poincaré group) on the superspace coordinates, and we begin by noting that any $SP$ transformation can effectively be written in the following way without the boosts and rotations of the Lorentz group:
\[g_0(a,\alpha) = \exp[ia^\mu P_\mu + i\alpha^AQ_A +i\bar{\alpha}_{\dot{A}}\bar{Q}^{\dot{A}}],\]
effectively setting $\omega_{\rho\nu}=0$, because we can again show that\footnote{Fortunately we are not going to do this because it is messy, but it can be done using the algebra of the group and the series expansion of the exponential function. Note, however, that the proof rests on the $P$s and $Q$s forming a closed set, which we saw in the algebra Eqs.~(\ref{eq:QPweyl})--(\ref{eq:QQbarweyl}).}
\begin{equation}
\exp\left[\frac{i}{2}\omega_{\rho\nu}M^{\rho\nu}\right]g_0(a,\alpha) = g_0(\Lambda a,S(\Lambda)\alpha)\exp\left[\frac{i}{2}\omega_{\rho\nu}M^{\rho\nu}\right],
\end{equation}
{\it i.e.}\ that all that a Lorentz boost does is to transform spacetime coordinates by $\Lambda$ and Weyl spinors by $S(\Lambda)$, which is the spinor representation of $\Lambda$ ($SL(2,\mathbb C)$). Thus, in more colloquial terms, for the supersymmetry transformation it does not matter which reference frame we are working in, we know how the transformation changes between the frames, given by  $\Lambda a$  and $S(\Lambda)\alpha$.

@@

In moving the problem to the exponential, we can use the power of some results on the exponentials of non-commuting quantities, in particular the Campbell-Baker-Hausdorff expansion from (\ref{eq:BKH_matrices}).
We have\footnote{Here we use Campbell-Baker-Hausdorff expansion $e^{A}e^{B} = e^{A + B + \frac{1}{2}[A, B] + ...}$ where the terms that follow all contain commutators of the first commutator  $[A, B] $ and the operators $A$ and $B$.}

@@

The commutator is proportional with $P_\mu$, and will therefore commute with all the operators in the problem, in particular the higher terms in the Campbell-Baker-Hausdorff expansion, meaning that the series reduces to

@@

As a crucial by-product we can now write down a differential representation for the supersymmetry generators by applying the standard expression for the generators $X_i$ of a Lie algebra, given the composition functions $f_\pi$:
\[ iX_j = \frac{\partial f_\pi}{\partial a_j}\frac{\partial}{\partial z_\pi},\]
which gives us:
\begin{eqnarray}
iP_\mu &=& \partial_\mu \label{eq:diffrepP},\\
iQ_A &=& -i(\sigma^\mu\bar{\theta})_A\partial_\mu +\partial_A,\\
i\bar{Q}^{\dot{A}} &=& -i(\bar{\sigma}^\mu \theta)^{\dot{A}}\partial_\mu +\partial^{\dot{A}}.
\label{eq:diffrepQbar}
\end{eqnarray}
The interested reader can now use these expressions to check the (anti-)commutation relations for the supercharges in Eqs.~(\ref{eq:QQweyl}) and (\ref{eq:QQbarweyl}).

@@

As Grassmann numbers the superspace coordinates obey the following commutation rules:
\[\{\theta_A, \theta_B\} = \{\theta_A, \bar{\theta}_{\dot{B}}\} = \{ \bar{\theta}_{\dot{A}}, \theta_B\} = \{\bar{\theta}_{\dot{A}}, \bar{\theta}_{\dot{B}}\} =0.\]
From this we get the relationships:\footnote{There is no summation implied in the first two lines, only a repetition of the same superspace coordinate. These are of course the same relations we already used for the Weyl spinors.}
\begin{eqnarray}
\theta_A^2 &=& \theta_A \theta_A = -\theta_A \theta_A = 0, \label{eq:thetasq}\\
\bar{\theta}_{\dot{A}}^2 &=& \bar{\theta}_{\dot{A}}\bar{\theta}_{\dot{A}} = -\bar{\theta}_{\dot{A}}\bar{\theta}_{\dot{A}} = 0, \\
\theta^2 &\equiv& \theta\theta \equiv \theta^A\theta_A = -2\theta_1\theta_2,\\
\bar{\theta}^2 &\equiv& \bar{\theta}\bar{\theta} \equiv \bar{\theta}_{\dot{A}}\bar{\theta}^{\dot{A}} = 2\bar{\theta}^{\dot{1}}\bar{\theta}^{\dot{2}}.
\end{eqnarray}
Notice that if we have a function $f$ of a Grassman number, say $\theta_A$, then the all-order expansion of that function in terms of $\theta_A$, is
\begin{equation}
f(\theta_A) = a_0 + a_1 \theta_A,\label{eq:fexp}
\end{equation}
as there are simply no more terms because of (\ref{eq:thetasq}).

We now need to define differentiation and integration on these numbers in order to create a calculus for them.\footnote{These definitions have no infinitesimal interpretations, nor is there any separate notion of definite integrals.}
\df{We define differentiation in superspace  by:
\[\partial_A \theta^B \equiv \frac{\partial}{\partial \theta^A} \theta^B \equiv \delta_A{}^B,\]
with a product rule
\begin{eqnarray}
\partial_A(\theta^{B_1} \theta^{B_2}\theta^{B_3}\ldots\theta^{B_n} ) &\equiv& (\partial_A\theta^{B_1}) \theta^{B_2}\theta^{B_3}\ldots\theta^{B_n}\nonumber\\
&&- \theta^{B_1}(\partial_A\theta^{B_2})\theta^{B_3}\ldots\theta^{B_n}\nonumber\\
 && +\ldots+(-1)^{n-1}\theta^{B_1}\theta^{B_2}\ldots(\partial_A\theta^{B_n}).
 \end{eqnarray}}
 This implies that the differential operator $\partial_A$ is itself a Grassmann number and anti-commutes. We can show that the indices of these operators can be raised and lowered with the $\epsilon$ in Eqs.~(\ref{eq:epsilonAB}) and (\ref{eq:epsilonAdotBdot}).

\df{The integral of a function $f$ of a superspace coordinate $\theta_A$ is defined as a functional $I[f]$
\[ I[f]=\int d\theta_A \, f(\theta_A), \]
which evaluates to a {\bf $\mathbf c$-number} (number in $\mathbb C$). The evaluation is defined by the relations
 \[\int d\theta_A \equiv 0,\quad \int d\theta_A \, \theta_A \equiv 1,\] 
and similarly for $\bar\theta_{\dot A}$, and we demand linearity:
\[\int d\theta_A[af(\theta_A) + bg(\theta_A)] \equiv a\int d\theta_A f(\theta_A) + b\int d\theta_A g(\theta_A).\]
In these definitions there is no implied summation over the index $A$.}

@@

To integrate over multiple Grassmann numbers we define volume elements as
\begin{eqnarray*}
d^2\theta &\equiv& -\frac{1}{4}d\theta^Ad\theta_A,\\
d^2\bar{\theta} &\equiv& -\frac{1}{4}d\bar{\theta}_{\dot{A}}d\bar{\theta}^{\dot{A}},\\
d^4\theta &\equiv& d^2\theta d^2\bar{\theta},
\end{eqnarray*}
and we demand that the integral operators anti-commute, just as the differential operators
\[ \{\int d\theta_A,\int d\theta_B\}=\{\int d\theta_A,\theta_B\}=0.\]
This specific volume element definition is made to normalise the following integrals
\begin{eqnarray*}
\int d^2\theta\text{ }\theta\theta &=& 1,\\
\int d^2\bar{\theta}\text{ }\bar{\theta} \bar{\theta} &=& 1,\\
\int d^4 \theta \text{ }(\theta\theta)(\bar{\theta} \bar{\theta}) &=& 1.
\end{eqnarray*}

@@

%%%%%%%%%%%%%%%
\section{Covariant derivatives}
\label{sec:covder}
%%%%%%%%%%%%%%%
Similar to the properties of covariant derivatives for gauge transformations in gauge theories, it would be nice to have a derivative that is invariant under supersymmetry transformations, {\it i.e.}\ commutes with the supersymmetry generators. Obviously $P_\mu = -i\partial_\mu$ does this, but more general covariant derivatives can be made.
\df{The following {\bf covariant derivatives} commute with supersymmetry transformations:
\begin{eqnarray}
D_A &\equiv& \partial_A + i(\sigma^\mu\bar{\theta})_A\partial_\mu ,\\
\bar{D}_{\dot{A}} &\equiv& -\partial_{\dot{A}}-i(\theta\sigma^\mu)_{\dot{A}}\partial_\mu.
\end{eqnarray}}

@@

%%%%%%%%%%
\section{Superfields}
%%%%%%%%%%
Using the superspace coordinates we can now define functions of these to use in a field theory. Naturally we should call these objects superfields.
\df{A {\bf superfield} $\Phi$ is an operator valued function on superspace $\Phi(x, \theta, \bar{\theta})$.}
Notice how we write, just as for ordinary fields depending on four-vector coordinates, the coordinates sans indices.

We can expand any such superfield $\Phi(x, \theta, \bar{\theta})$  as a power series in $\theta$ and $\bar{\theta}$. For a superfield without explicit spinor indices this gives in general,
%\footnote{Equation (\ref{eq:gen_sup}) can be shown to be closed under supersymmetry transformations, meaning that a superfield transforms into another superfield under the transformations of the previous section.}
\begin{eqnarray}
\Phi(x, \theta, \bar{\theta}) &=& f(x) + \theta^A\phi_A(x) + \bar{\theta}_{\dot{A}}\bar{\chi}^{\dot{A}}(x) + \theta\theta m(x) + \bar{\theta}\bar{\theta}n(x) \nonumber\\ 
&& + \theta \sigma^\mu \bar{\theta}V_\mu(x) + \theta \theta \bar{\theta}_{\dot{A}}\bar{\lambda}^{\dot{A}}(x) +\bar{\theta}\bar{\theta}\theta^A\psi_A(x) + \theta\theta\bar{\theta}\bar{\theta}d(x),\label{eq:gen_sup}
\end{eqnarray} 
where the functions of space-time coordinates $x$ are called the {\bf component fields}. Any superfield without explicit spinor indices, such as the one above, commutes with any other superfield, because all the Grassmann numbers appear in contracted pairs.

The properties of the component fields can be deduced from the requirement that $\Phi$ must be an (operator valued) Lorentz scalar or pseudoscalar. These are shown in Table~\ref{tab:gensup} along with the corresponding degrees of freedom each field has.
\begin{center}
   \begin{tabular}{c |l| c} 
   \noalign{\smallskip}\hline\noalign{\smallskip}
   {\bf Component field} & {\bf Type} & {\bf d.o.f.} \\
   \noalign{\smallskip}\hline\noalign{\smallskip}
   $f(x)$, $m(x)$, $n(x)$ & Complex (pseudo) scalar & 2\\
   $\psi_A(x)$, $\phi_A(x)$ & Left-handed Weyl spinor & 4\\
   $\bar{\chi}^{\dot{A}}(x)$, $\bar{\lambda}^{\dot{A}}(x)$ &Right-handed Weyl spinor& 4\\
   $V_\mu(x)$ & Lorentz 4-vector (complex) & 8\\
   $d(x)$ & Complex scalar & 2 \\
   \noalign{\smallskip}\hline\noalign{\smallskip}
    \end{tabular}
   \captionof{table}{Component field content of a general superfield. \label{tab:gensup}}
   \end{center}

One can show that under supersymmetry transformations these component fields transform linearly into each other, thus we say that superfields (with the differential form of the supersymmetry generators) are {\it representations} of the super-Poincar\'e group -- in the sense of being states in a representation space -- just as ordinary quantum fields are representations of the Poincaré group, albeit {\it highly reducible} representations since there are subsets of the component fields that are closed on the supersymmetry transformation!\footnote{Indeed, they are linear representations since a sum of superfields is a superfield, and the differential supersymmetry operators act linearly.} 
%We often write the supersymmetry transformation as
%\[ \delta_S=(i\theta Q+i\bar\theta \bar Q), \] 
%as the translation part is `trivial' and its generators in any case commutes with the $Q$s. 
For example, the scalar fields $f$ and $m$, and the Weyl-spinor $\phi$ transform as\footnote{A word of warning is in order here. Considering $\Phi$ as a {\it quantum} field with operator value it transforms under the supersymmetry transformations in the {\it passive sense}  
\[ \Phi(x)\to \exp{(-i\alpha Q-i\bar\alpha \bar Q)}\Phi(x)\exp{(i\alpha Q+i\bar\alpha \bar Q)}. \]}
\begin{eqnarray}
\delta_S f &=& \alpha\phi +\bar\alpha\bar\chi, \\
\delta_S\phi_A &=& 2 \alpha_A m + (\sigma^\mu \bar\alpha)_A (i\partial_\mu f + V_\mu), \\
\delta_S m &=& \bar\alpha\bar\lambda-\frac{i}{2}\partial_\mu\phi\sigma^\mu\bar\alpha .
\label{eq:general_superfield_transform}
\end{eqnarray}
% TODO: Add some more examples of the actual transforms here

We can recover the known irreducible representations, see Section~\ref{sec:superalgebrarep}, by imposing some restrictions on the fields. To do this we define the following three types of superfields that we will discuss below:
\begin{eqnarray}
\bar{D}_{\dot{A}}\Phi(x, \theta, \bar{\theta}) =& 0 &\quad\text{({\bf left-handed scalar superfield})}\label{eq:leftsup}\\
D_{A}\Phi^\dagger (x, \theta, \bar{\theta}) =& 0 &\quad\text{(\bf{right-handed scalar superfield})}\label{eq:rightsup}\\
\Phi^\dagger (x, \theta, \bar{\theta}) =& \Phi(x, \theta, \bar{\theta}) &\quad\text{({\bf vector superfield})}
\end{eqnarray}
Note that it is $\Phi^\dagger$ which is the right-handed superfield in Eq.~(\ref{eq:rightsup}), not $\Phi$. However, we can show that the hermitian conjugate of a left-handed scalar superfield fulfils the condition for a right-handed scalar superfield. We always keep the ``dagger'' operator on the right-handed fields to remember what they are since the difference between left- and right-handed superfields will become crucial later. Supersymmetry transformations can also be shown to transform left-handed superfields into left-handed superfields, right-handed superfields into right-handed superfields and vector superfields into vector superfields. This means that they are separate representations.

Products of the same type of superfield is a superfield of the same type since for left-handed scalar superfields $\Phi_i$ and $\Phi_j$,
\[ \bar{D}_{\dot{A}}(\Phi_i\Phi_j) = (\bar{D}_{\dot{A}}\Phi_i)\Phi_j +\Phi_i( \bar{D}_{\dot{A}}\Phi_j)=0,\]
and similarly for a right-handed scalar superfields, and for vector superfields $\Phi_i$ and $\Phi_j$,
\[(\Phi_i\Phi_j)^\dagger=\Phi_j^\dagger \Phi_i^\dagger=\Phi_j \Phi_i= \Phi_i\Phi_j.\]
The product of a left-handed scalar superfield $\Phi$ and its hermitian conjugate $\Phi^\dagger$, $V=\Phi \Phi^\dagger$, is a vector superfield since
\[V^\dagger=(\Phi \Phi^\dagger)^\dagger=\Phi \Phi^\dagger=V.\]
The same is true for sums of superfields of the same type. These properties will be important when creating a superfield version of a Lagrangian.
% TODO: Extend this to the idea of holonomic functions

>>>>

To understand what all of this means we start from the same perspective as for the four-vectors in the previous section, and begin by writing a general element of SP, $g\in SP$, using the exponential map defined in Section \ref{sec:lie_algebras}:
\[g = \exp\left(ix^\mu P_\mu + i\theta^{A} Q_A + i\bar{\theta}_{\dot{A}}\bar{Q}^{\dot{A}} + \frac{i}{2}\omega_{\mu\nu}M^{\mu\nu}\right),\]
where $x^\mu$, $\theta^{A}$, $\bar{\theta}_{\dot{A}}$ and $\omega_{\mu\nu}$ constitute the parametrisation of the group, and $P_\mu$, $Q_A$, $\bar Q^{\dot{A}}$ and $M_{\mu\nu}$ are the generators. Following the same argument as above we can now parametrise the coset space $SP/L$ simply by setting $\omega_{\mu\nu} = 0$.\footnote{$SP/L$ is again {\it not} a coset group, because $L$ is not a normal subgroup of $SP$, but it still forms a vector space (the coset space) which we call superspace.} The remaining parameters of $SP/L$ are then the coordinates that span superspace.

@@

We now want to find the effect of supersymmetry transformations (transformations by the super-Poincaré group) on the superspace coordinates, and we begin by noting that any $SP$ transformation can effectively be written in the following way without the boosts and rotations of the Lorentz group:
\[g_0(a,\alpha) = \exp[ia^\mu P_\mu + i\alpha^AQ_A +i\bar{\alpha}_{\dot{A}}\bar{Q}^{\dot{A}}],\]
effectively setting $\omega_{\rho\nu}=0$, because we can again show that\footnote{Fortunately, we are not going to do this here because it is messy, but it can be done using the algebra of the group and the series expansion of the exponential function. Note, however, that the proof rests on the $P$s and $Q$s forming a closed set, which we saw in the algebra Eqs.~(\ref{eq:QPweyl})--(\ref{eq:QQbarweyl}).}
\begin{equation}
\exp\left[\frac{i}{2}\omega_{\mu\nu}M^{\mu\nu}\right]g_0(a,\alpha) = g_0(\Lambda a,S(\Lambda)\alpha)\exp\left[\frac{i}{2}\omega_{\mu\nu}M^{\mu\nu}\right],
\end{equation}
{\it i.e.}\ that all that a Lorentz boost does is to transform spacetime coordinates by $\Lambda$ and Weyl spinors by $S(\Lambda)$, which is the spinor representation of $\Lambda$ ($SL(2,\mathbb C)$). Thus, in more colloquial terms, for the supersymmetry transformation it does not matter which reference frame we are working in, we know how the transformation changes between the frames, given by  $\Lambda a$  and $S(\Lambda)\alpha$.

@@

In moving the problem to the exponential, we can use the power of some results on the exponentials of non-commuting quantities, in particular the Campbell--Baker--Hausdorff expansion from (\ref{eq:BKH_matrices}).
We have\footnote{Here we use Campbell--Baker--Hausdorff expansion $e^{A}e^{B} = e^{A + B + \frac{1}{2}[A, B] + ...}$ where the terms that follow all contain commutators of the first commutator  $[A, B] $ and the operators $A$ and $B$.}

@@

The commutator is proportional with $P_\mu$, and will therefore commute with all the operators in the problem, in particular the higher terms in the Campbell--Baker--Hausdorff expansion, meaning that the series reduces to

@@

As a crucial by-product we can now write down a differential representation for the supersymmetry generators by applying the standard expression for the generators $X_i$ of a Lie algebra, given the composition functions $f_\pi$:
\[ iX_j = \frac{\partial f_\pi}{\partial a_j}\frac{\partial}{\partial z_\pi},\]
which gives us:
\begin{eqnarray}
iP_\mu &=& \partial_\mu \label{eq:diffrepP},\\
iQ_A &=& -i(\sigma^\mu\bar{\theta})_A\partial_\mu +\partial_A,\\
i\bar{Q}^{\dot{A}} &=& -i(\bar{\sigma}^\mu \theta)^{\dot{A}}\partial_\mu +\bar\partial^{\dot{A}}.
\label{eq:diffrepQbar}
\end{eqnarray}
The interested reader can now use these expressions to check the (anti-)commutation relations for the supercharges in Eqs.~(\ref{eq:QQweyl}) and (\ref{eq:QQbarweyl}).

@@

As Grassmann numbers the superspace coordinates obey the following commutation rules:
\[\{\theta_A, \theta_B\} = \{\theta_A, \bar{\theta}_{\dot{B}}\} = \{ \bar{\theta}_{\dot{A}}, \theta_B\} = \{\bar{\theta}_{\dot{A}}, \bar{\theta}_{\dot{B}}\} =0.\]
From this we get the relationships:\footnote{There is no summation implied in the first two lines, only a repetition of the same superspace coordinate. These are of course the same relations we already used for the Weyl spinors.}
\begin{eqnarray}
\theta_A^2 &=& \theta_A \theta_A = -\theta_A \theta_A = 0, \label{eq:thetasq}\\
\bar{\theta}_{\dot{A}}^2 &=& \bar{\theta}_{\dot{A}}\bar{\theta}_{\dot{A}} = -\bar{\theta}_{\dot{A}}\bar{\theta}_{\dot{A}} = 0, \\
\theta^2 &\equiv& \theta\theta \equiv \theta^A\theta_A = -2\theta_1\theta_2,\\
\bar{\theta}^2 &\equiv& \bar{\theta}\bar{\theta} \equiv \bar{\theta}_{\dot{A}}\bar{\theta}^{\dot{A}} = 2\bar{\theta}^{\dot{1}}\bar{\theta}^{\dot{2}}.
\end{eqnarray}
Notice that if we have a function $f$ of a single Grassmann number, say the superspace coordinate $\theta_A$, then that function can be written
\begin{equation}
f(\theta_A) = a_0 + a_1 \theta_A,\label{eq:fexp}
\end{equation}
as there are simply no more terms because of (\ref{eq:thetasq}).

We now need to define differentiation and integration on these numbers in order to create a calculus for them.\footnote{These definitions have no infinitesimal interpretations, nor is there any separate notion of definite integrals.}
\df{We define differentiation in superspace  by:
\[\partial_A \theta^B \equiv \frac{\partial}{\partial \theta^A} \theta^B \equiv \delta_A{}^B,\quad  \bar\partial_{\dot{A}} \bar\theta^{\dot B} \equiv \frac{\partial}{\partial \bar\theta^{\dot A}} \bar\theta^{\dot B} \equiv \delta_{\dot A}{}^{\dot B}\]
with a product rule due to the anti-commuting nature of the superspace coordinates
\begin{eqnarray}
\partial_A(\theta_1^{B_1} \theta_2^{B_2}\theta_3^{B_3}\ldots\theta_n^{B_n} ) &\equiv& (\partial_A\theta_1^{B_1}) \theta_2^{B_2}\theta_3^{B_3}\ldots\theta_n^{B_n}\nonumber\\
&&- \theta_1^{B_1}(\partial_A\theta_2^{B_2})\theta_3^{B_3}\ldots\theta_n^{B_n}\nonumber\\
 && +\ldots+(-1)^{n-1}\theta_1^{B_1}\theta_2^{B_2}\ldots(\partial_A\theta_n^{B_n}),
\label{eq:superspace_diff_product_rule}
 \end{eqnarray}
and similarly for $\bar\partial$.}
This implies that the differential operator $\partial_A$ is itself a Grassmann number and anti-commutes 
\[\{\partial_A, \partial_B\} = \{\partial_A, \bar\partial_{\dot{B}}\} = \{ \bar\partial_{\dot{A}}, \partial_B\} = \{\bar\partial_{\dot{A}}, \bar\partial_{\dot{B}}\} =0.\]
However, notice that by (\ref{eq:superspace_diff_product_rule})
\[ \{\partial_A, \theta_B\}=\partial_A\theta_B- \theta_B\partial_A +\theta_B\partial_A =  \delta_{AB},\]
and similar relations. We can show that the indices of these differential operators can be raised and lowered with the $\epsilon$ in Eqs.~(\ref{eq:epsilonAB}) and (\ref{eq:epsilonAdotBdot}).

\df{The integral operator of a function $f$ of a superspace coordinate $\theta_A$ is defined as a functional $I[f]$
\[ I[f]=\int d\theta_A \, f(\theta_A), \]
which evaluates to a {\bf $\mathbf c$-number} (number in $\mathbb C$). The evaluation is defined by the relations
 \[\int d\theta_A \equiv 0,\quad \int d\theta_A \, \theta_A \equiv 1,\] 
and similarly for $\bar\theta_{\dot A}$. We demand linearity:
\[\int d\theta_A[af(\theta_A) + bg(\theta_A)] \equiv a\int d\theta_A f(\theta_A) + b\int d\theta_A g(\theta_A),\]
and that the integral operators anti-commute, just as the differential operators
\[ \{\int d\theta_A,\int d\theta_B\}=\{\int d\theta_A,\theta_B\}=0.\]
}

@@

To integrate over multiple superspace coordinates we define volume elements as
\begin{eqnarray*}
d^2\theta &\equiv& -\frac{1}{4}d\theta^Ad\theta_A,\\
d^2\bar{\theta} &\equiv& -\frac{1}{4}d\bar{\theta}_{\dot{A}}d\bar{\theta}^{\dot{A}},\\
d^4\theta &\equiv& d^2\theta d^2\bar{\theta}.
\end{eqnarray*}
This specific volume element definition is made to normalise the following integrals
\begin{eqnarray*}
\int d^2\theta\text{ }\theta\theta &=& 1,\\
\int d^2\bar{\theta}\text{ }\bar{\theta} \bar{\theta} &=& 1,\\
\int d^4 \theta \text{ }(\theta\theta)(\bar{\theta} \bar{\theta}) &=& 1.
\end{eqnarray*}

@@

%%%%%%%%%%%%%%%
\section{Covariant derivatives}
\label{sec:covder}
%%%%%%%%%%%%%%%
Similar to the properties of covariant derivatives for gauge transformations in gauge theories,\footnote{Under a local gauge transformation $U(x)$ a gauge covariant derivative $D_\mu$ acting on a field $\phi(x)$ transforms as $D_\mu\phi(x)\to D'_\mu\phi'(x)=D_\mu U(x)\phi(x)=U(x)D_\mu \phi(x)$, or $D'_\mu=U(x)D_\mu U^{-1}(x)$.} it would be nice to have a derivative that is invariant under supersymmetry transformations, {\it i.e.}\ commutes with the supersymmetry generators. Obviously $P_\mu = -i\partial_\mu$ does this, but more general covariant derivatives can be made.
\df{The following {\bf covariant derivatives} commute with supersymmetry transformations:
\begin{eqnarray}
D_A &\equiv& \partial_A + i(\sigma^\mu\bar{\theta})_A\partial_\mu ,\\
\bar{D}_{\dot{A}} &\equiv& -\bar\partial_{\dot{A}}-i(\theta\sigma^\mu)_{\dot{A}}\partial_\mu.
\end{eqnarray}}

@@

%%%%%%%%%%
\section{Superfields}
%%%%%%%%%%
Using the superspace coordinates we can now define functions of these to use in a field theory. Naturally we should call these objects superfields.
\df{A {\bf superfield} $\Phi$ is a function on superspace $\Phi(x, \theta, \bar{\theta})$.}
Notice how we write, just as for ordinary fields depending on four-vector coordinates, the coordinates sans indices.

We can expand any such superfield $\Phi(x, \theta, \bar{\theta})$  as a power series in $\theta$ and $\bar{\theta}$. For a superfield without explicit spinor indices this gives in general,
\begin{eqnarray}
\Phi(x, \theta, \bar{\theta}) &=& f(x) + \theta^A\phi_A(x) + \bar{\theta}_{\dot{A}}\bar{\chi}^{\dot{A}}(x) + \theta\theta m(x) + \bar{\theta}\bar{\theta}n(x) \nonumber\\ 
&& + \theta \sigma^\mu \bar{\theta}V_\mu(x) + \theta \theta \bar{\theta}_{\dot{A}}\bar{\lambda}^{\dot{A}}(x) +\bar{\theta}\bar{\theta}\theta^A\psi_A(x) + \theta\theta\bar{\theta}\bar{\theta}d(x),\label{eq:gen_sup}
\end{eqnarray} 
where the functions of space-time coordinates $x$ are called the {\bf component fields}. Any superfield without explicit spinor indices, such as the one above, commutes with any other superfield, because all the Grassmann numbers appear in contracted pairs.

The properties of the component fields can be deduced from the requirement that $\Phi$ must be an (operator valued) Lorentz scalar or pseudoscalar. These are shown in Table~\ref{tab:gensup} along with the corresponding degrees of freedom each field has.
\begin{table}
\begin{center}
   \begin{tabular}{c |l| c} 
   \noalign{\smallskip}\hline\noalign{\smallskip}
   {\bf Component field} & {\bf Type} & {\bf d.o.f.} \\
   \noalign{\smallskip}\hline\noalign{\smallskip}
   $f(x)$, $m(x)$, $n(x)$ & Complex (pseudo) scalar & 2\\
   $\psi_A(x)$, $\phi_A(x)$ & Left-handed Weyl spinor & 4\\
   $\bar{\chi}^{\dot{A}}(x)$, $\bar{\lambda}^{\dot{A}}(x)$ &Right-handed Weyl spinor& 4\\
   $V_\mu(x)$ & Lorentz 4-vector (complex) & 8\\
   $d(x)$ & Complex scalar & 2 \\
   \noalign{\smallskip}\hline\noalign{\smallskip}
    \end{tabular}
   \caption{Component field content of a general superfield. \label{tab:gensup}}
\end{center}
\end{table}

One can show that under supersymmetry transformations these component fields transform linearly into each other. Under the infinitesimal transformation $\delta_S=i\alpha Q+i\bar\alpha \bar Q$ we have\footnote{If a component field $f$ transforms as $f\to f' \equiv f+\delta_sf$ under the supersymmetry transformation then \[\delta_sf= f'-f =e^{i\alpha Q+i\bar\alpha\bar Q}f -f=(i\alpha Q+i\bar\alpha \bar Q)f, \] for infinitesimal transformation parameters.}\footnote{A word of warning is in order here. Considering $\Phi$ as a {\it quantum} superfield with operator valued component fields it transforms under the supersymmetry transformations in the {\it passive sense}  
\[ \Phi(x)\to \Phi'(x)=\exp{(-i\alpha Q-i\bar\alpha \bar Q)}\Phi(x)\exp{(i\alpha Q+i\bar\alpha \bar Q)}. \]}
\begin{eqnarray}
\delta_S f &=& \alpha\phi +\bar\alpha\bar\chi, \label{eq:general_superfield_f_component_transform} \\
\delta_S\phi_A &=& 2 \alpha_A m + (\sigma^\mu \bar\alpha)_A (i\partial_\mu f + V_\mu), \\
\delta_S\bar\chi^{\dot A} &=& 2 \bar\alpha^{\dot A} n + (\alpha \sigma^\mu)^{\dot A} (i\partial_\mu f - V_\mu), \\
\delta_S m &=& \bar\alpha\bar\lambda-\frac{i}{2}\partial_\mu\phi\sigma^\mu\bar\alpha, \\
\delta_S n &=& \alpha\psi+\frac{i}{2}\alpha\sigma^\mu\partial_\mu\bar\chi, \\
\delta_S V &=& \alpha\sigma_\mu\bar\lambda + \psi\sigma_\mu\bar\alpha + \frac{i}{2}\alpha\partial_\mu\phi -\frac{i}{2}\partial_\mu\bar\chi\bar\alpha, \\
\delta_S\bar\lambda^{\dot A} &=& 2\bar\alpha^{\dot A} d+\frac{i}{2}\bar\alpha^{\dot A}\partial^\mu V_\mu+i(\alpha\sigma^\mu)^{\dot A}\partial_\mu m, \\
\delta_S\psi_A &=& 2\alpha_A d-\frac{i}{2}\alpha_A \partial^\mu V_\mu+i(\sigma^\mu\bar\alpha)_A \partial_\mu n, \\
\delta_S d  &=& \frac{i}{2}\partial_\mu\psi\sigma^\mu\bar\alpha-\frac{i}{2}\partial_\mu\bar\lambda\bar\sigma^\mu\alpha. \label{eq:general_superfield_d_component_transform}
\end{eqnarray}
Thus we say that superfields (with the differential form of the supersymmetry generators) are {\it representations} of the super-Poincar\'e group---in the sense of being states in a representation space---just as ordinary quantum fields are representations of the Poincaré group, albeit {\it highly reducible} representations since there are subsets of the component fields that are closed on the supersymmetry transformation!\footnote{Indeed, they are also linear representations since a sum of superfields is a superfield, and the differential supersymmetry operators act linearly.}

We can recover the known irreducible representations, see Section~\ref{sec:superalgebrarep}, by imposing some restrictions on the fields. To do this we define the following three types of superfields that we will discuss below:
\begin{eqnarray}
\bar{D}_{\dot{A}}\Phi(x, \theta, \bar{\theta}) =& 0 &\quad\text{({\bf left-handed scalar superfield})}\label{eq:leftsup}\\
D_{A}\Phi^\dagger (x, \theta, \bar{\theta}) =& 0 &\quad\text{(\bf{right-handed scalar superfield})}\label{eq:rightsup}\\
V^\dagger (x, \theta, \bar{\theta}) =& V(x, \theta, \bar{\theta}) &\quad\text{({\bf vector superfield})}
\end{eqnarray}
Note that it is $\Phi^\dagger$ which is the right-handed superfield in Eq.~(\ref{eq:rightsup}), not $\Phi$. However, we can show that the hermitian conjugate of a left-handed scalar superfield fulfils the condition for a right-handed scalar superfield. We always keep the ``dagger'' operator on the right-handed fields to remember what they are since the difference between left- and right-handed superfields will become crucial later. Supersymmetry transformations can also be shown to transform left-handed superfields into left-handed superfields, right-handed superfields into right-handed superfields and vector superfields into vector superfields. This means that they are separate representations.

Products of the same type of superfield is a superfield of the same type since for left-handed scalar superfields $\Phi_i$ and $\Phi_j$,
\[ \bar{D}_{\dot{A}}(\Phi_i\Phi_j) = (\bar{D}_{\dot{A}}\Phi_i)\Phi_j +\Phi_i( \bar{D}_{\dot{A}}\Phi_j)=0,\]
and similarly for a right-handed scalar superfields, and for vector superfields $V_i$ and $Vi_j$,
\[(V_iV_j)^\dagger=V_j^\dagger V_i^\dagger=V_j V_i= V_iV_j.\]
The product of a left-handed scalar superfield $\Phi$ and its hermitian conjugate $\Phi^\dagger$, $V=\Phi \Phi^\dagger$, is a vector superfield since
\[V^\dagger=(\Phi \Phi^\dagger)^\dagger=\Phi \Phi^\dagger=V.\]
The same is true for sums of superfields of the same type. These properties will be important when creating a superfield version of a Lagrangian.
% TODO: Extend this to the idea of holonomic functions
